Elephant Seal Age JAE Intraspecific Variation

### 2023-11-13 paper/paperv2.qmd
modeling offspring metrics quadratically

**Note**: *statistics for increase in inter-birth interval?*

@@

**To do:** *Add sample sizes to the plot because they are different than Figure 1.* *Do I need to do this if I have the sample sizes in the manuscript?*

@@

>>>>

@@

@@

Modeling the above metrics as quadratic, just in case:

```{r}
surv_dat <- sealdat %>% filter(pupyearborn < 2016)
pup_survival_model <- glmer(pup_survived ~ poly(age, 2) + (1 | animalID) + (1 | year),
                            data = surv_dat,
                            family = "binomial")
summary(pup_survival_model)

pup_recruit_model <- glmer(puprecruited ~ poly(age, 2) + (1 | animalID) + (1 | year),
                           data = filter(sealdat, year > 1984), 
                           family = "binomial")
summary(pup_recruit_model)

Neither were significant as 2nd order polynomials.
